Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-02-20 Draft/distributionsNLO.tex
Many changes from Ansgar and Mathieu

We start with Fig.~\ref{fig:distNLO1} which displays the invariant mass (top) and the rapidity separation (bottom) of the two tagging jets.
For high invariant mass, all predictions agree rather well.
On the other hand, for low invariant mass, the hierarchy present at the level of the cross section is here reproduced.
The VBS-approximated predictions ({\sc Bonsay} and the {\sc Powheg-Box}) are lower than the full calculation ({\sc MoCaNLO}+{\sc Recola}).
The full calculation is rather well approximated by the hybrid VBS approximation implemented in {\sc MadGraph5\_aMC\-@NLO}.
Finally, {\sc VBFNLO} which includes as well $s$-channel contributions provides larger predictions at low invariant mass.
For the rapidity difference between the two tagging jets, the hierarchy between the predictions is rather similar.

 \begin{figure*}[hbt!]
   \centering
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/mjj_NLO.pdf}
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/dyj1j2_NLO.pdf}
\caption{\label{fig:distNLO1} Differential distributions in the invariant mass (top) and rapidity difference of the two tagging jets (bottom).
The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
\MP{MG statistics should be improved and the baseline changed to Recola.}
}
\end{figure*}

Concerning the transverse momentum (top) and rapidity (bottom) of the hardest jet shown in Fig.~\ref{fig:distNLO2}, the situation is rather different.
While {\sc MadGraph5\_aMC\-@NLO} is very close to the full prediction for low transverse momentum, it is diverging from it at larger transverse momentum.
This is in contrast with {\sc Bonsay} and {\sc Powheg} which approximate the full computation reasonably well over the whole range and in particular in the high transverse-momentum region.
Finally, {\sc VBFNLO} predicts higher rates over the whole range apart from around $200\GeV$ where it is in perfect agreement with the complete calculation.
Concerning the rapidity of the hardest jet, {\sc VBFNLO} is in good agreement with {\sc MoCaNLO}+{\sc Recola} in the rapidity range $|y_{j_1}| < 3$.
For larger rapidity, the other codes constitute a better description of the full process at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.

 \begin{figure*}[hbt!]
   \centering
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/ptj1_NLO.pdf}
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/yj1_NLO.pdf}
\caption{\label{fig:distNLO2} Differential distributions in the transverse momentum (top) and rapidity of the hardest jet (bottom).
The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
\MP{MG statistics should be improved and the baseline changed to Recola.}
}
\end{figure*}

The last set of differential distributions is the invariant mass of the two charged lepton (top) and the Zeppenfeld variable for the anti-muon (bottom).
Concerning the comparison of the predictions, both distributions display a rather similar behaviour.
Indeed, the hierarchy mentioned previously is here respected and enhanced towards high invariant mass or high Zeppenfeld variable.
{\sc MoCaNLO}+{\sc Recola} and {\sc VBFNLO} are in rather good agreement for both distributions for the kinematic range displayed here.
The other three VBS approximations are close to each other within few per cent.

 \begin{figure*}[hbt!]
   \centering
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/mll_NLO.pdf}
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/zmu_NLO.pdf}
\caption{\label{fig:distNLO3} Differential distributions in the invariant mass of the two charged leptons (top) and Zeppenfeld variable for the muon (bottom).
The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
The upper plots provides the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
\MP{MG statistics should be improved and the baseline changed to Recola.}
}
\end{figure*}

>>>>

We start with Fig.~\ref{fig:distNLO1} which displays the invariant mass (left) and the rapidity separation (right) of the two tagging jets.
For high invariant mass, all predictions agree rather well.
On the other hand, for low invariant mass, the hierarchy present at the level of the cross section is here reproduced.
The VBS-approximated predictions ({\sc Bonsay} and the {\sc Powheg-Box}) are lower than the full calculation ({\sc MoCaNLO}+{\sc Recola}).
The full calculation is rather well approximated by the hybrid VBS approximation implemented in {\sc MadGraph5\_aMC\-@NLO}.
Finally, {\sc VBFNLO} which includes as well $s$-channel contributions provides larger predictions at low invariant mass.
For the rapidity difference between the two tagging jets, the hierarchy between the predictions is rather similar.

 \begin{figure*}[hbt!]
   \centering
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/mjj_NLO.pdf}
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/dyj1j2_NLO.pdf}
\caption{\label{fig:distNLO1} Differential distributions in the invariant mass (left) and rapidity difference of the two tagging jets (right).
The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
\MP{MG statistics should be improved and the baseline changed to Recola.}
}
\end{figure*}

Concerning the transverse momentum (left) and rapidity (right) of the hardest jet shown in Fig.~\ref{fig:distNLO2}, the situation is rather different.
While {\sc MadGraph5\_aMC\-@NLO} is very close to the full prediction for low transverse momentum, it is diverging from it at larger transverse momentum.
This is in contrast with {\sc Bonsay} and {\sc Powheg} which approximate the full computation reasonably well over the whole range and in particular in the high transverse-momentum region.
Finally, {\sc VBFNLO} predicts higher rates over the whole range apart from around $200\GeV$ where it is in perfect agreement with the complete calculation.
Concerning the rapidity of the hardest jet, {\sc VBFNLO} is in good agreement with {\sc MoCaNLO}+{\sc Recola} in the rapidity range $|y_{j_1}| < 3$.
For larger rapidity, the other codes constitute a better description of the full process at order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.

 \begin{figure*}[hbt!]
   \centering
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/ptj1_NLO.pdf}
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/yj1_NLO.pdf}
\caption{\label{fig:distNLO2} Differential distributions in the transverse momentum (left) and rapidity of the hardest jet (right).
The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
\MP{MG statistics should be improved and the baseline changed to Recola.}
}
\end{figure*}

The last set of differential distributions is the invariant mass of the two charged lepton (left) and the Zeppenfeld variable for the anti-muon (right).
Concerning the comparison of the predictions, both distributions display a rather similar behaviour.
Indeed, the hierarchy mentioned previously is here respected and enhanced towards high invariant mass or high Zeppenfeld variable.
{\sc MoCaNLO}+{\sc Recola} and {\sc VBFNLO} are in rather good agreement for both distributions for the kinematic range displayed here.
The other three VBS approximations are close to each other within few per cent.

 \begin{figure*}[hbt!]
   \centering
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/mll_NLO.pdf}
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/zmu_NLO.pdf}
\caption{\label{fig:distNLO3} Differential distributions in the invariant mass of the two charged leptons (left) and Zeppenfeld variable for the muon (right).
The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
\MP{MG statistics should be improved and the baseline changed to Recola.}
}
\end{figure*}

### 2018-02-20 Draft/input.tex
Many changes from Ansgar and Mathieu

The VBS production mechanism is simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$.
The NNPDF~3.0 parton density~\cite{Ball:2014uwa} with five flavour scheme, NLO QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ is employed.\footnote{The corresponding {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} is 260000.}
Since the employed PDF set has no photonic density, photon-induced processes are not considered.
Initial-state collinear singularities are factorised with the ${\overline{\rm MS}}$ scheme, consistently with what is done in NNPDF.

@@

\begin{itemize}
    \item The two same-sign charged leptons are required to have
        \begin{align}
        \label{cut:1}
         \ptsub{\Pl} >  20\GeV,\qquad |y_{\Pl}| < 2.5, \qquad \Delta R_{\Pl\Pl}> 0.3\,.
        \end{align}
    \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos, is required to be
        \begin{align}
        \label{cut:2}
          \etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
        \end{align}
    \item QCD partons (quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. Jets are required
        to have
        \begin{align}
        \label{cut:3}
         \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad \Delta R_{\Pj\Pl} > 0.3 \,.
        \end{align}
        VBS cuts are applied on the two jets with largest transverse-momentum, unless otherwise stated.
        These are an in\-vari\-ant mass cut on the di-jet system as well as rapidity-separation cut between the two jets.
        The nominal value of these cuts if not stated explicitly read:
        \begin{align}
        \label{cut:4}
         m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5.
        \end{align}
    \item When EW corrections are computed, real photons and charged fermion are clustered together using the anti-$k_T$ algorithm with
        radius parameter $R=0.1$. In this case, leptons and quarks are understood as {\it dressed fermions}.
\end{itemize}

>>>>

The partonic processes are simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$.
The NNPDF~3.0 parton density~\cite{Ball:2014uwa} with five flavour scheme, NLO QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ is employed.\footnote{The corresponding {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} is 260000.}
Since the employed PDF set has no photonic density, photon-induced processes are not considered.
Initial-state collinear singularities are factorised with the ${\overline{\rm MS}}$ scheme, consistently with what is done in NNPDF.

@@

\begin{itemize}
    \item The two same-sign charged leptons are required to have
        \begin{align}
        \label{cut:1}
         \ptsub{\Pl} >  20\GeV,\qquad |y_{\Pl}| < 2.5, \qquad \Delta R_{\Pl\Pl}> 0.3\,.
        \end{align}
    \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos, is required to be
        \begin{align}
        \label{cut:2}
          \etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
        \end{align}
    \item QCD partons (quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. Jets are required
        to have
        \begin{align}
        \label{cut:3}
         \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad \Delta R_{\Pj\Pl} > 0.3 \,.
        \end{align}
        VBS cuts are applied on the two jets with largest transverse-momentum, unless otherwise stated.
        These are an in\-vari\-ant mass cut on the di-jet system as well as rapidity-separation cut between the two jets.
        The nominal values of these cuts if not stated explicitly read:
        \begin{align}
        \label{cut:4}
         m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5.
        \end{align}
    \item When EW corrections are computed, real photons and charged fermions are clustered together using the anti-$k_T$ algorithm with
        radius parameter $R=0.1$. In this case, leptons and quarks are understood as {\it dressed fermions}.
\end{itemize}

### 2018-02-20 Draft/introduction.tex
Many changes from Ansgar and Mathieu

Vector-boson scattering (VBS) at a hadron collider 
usually refers to the interaction of massive vector-bosons ($\PW^\pm,\PZ$),
radiated by partons (quarks) of the incoming protons, 
which in turn are deflected from the beam direction 
and enter the volume of the particle detectors.
As a consequence, the typical signature of VBS events
is characterised by two energetic jets 
and four fermions,
originating from the decay of the two vector bosons.
Among the possible diagrams,
the scattering process can be mediated by a Higgs boson
and involve in particular their longitudinal component.
The interaction of longitudinally polarised bosons is of particular interest, 
because the corresponding matrix elements feature unitarity cancellations 
that strongly depend on the actual structure of the Higgs sector.
A detailed study of this class of processes will therefore further constrain the Higgs couplings 
at a very different energy scale with respect to the Higgs boson mass,
and hint at, or exclude, non-Standard Model behaviours.

The VBS process involving two same-sign $\PW$ bosons has the largest signal-to-background ratio at the LHC of all the VBS processes:
evidence for it was found at the centre-of-mass energy of $8~\TeV$ already~\cite{Aad:2014zda,Khachatryan:2014sta},
and it has been recently observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} 
at $13\TeV$ as well.
Presently, the measurements of VBS processes are limited by statistics, but the situation will change in the near future.
On the theoretical side, 
it is thus of prime importance to provide predictions with systematic uncertainties
at least comparable to the current and envisaged experimental precisions~\cite{CMS:2016rcn}.

$\PW^+\PW^+$ scattering is also the simplest VBS process to calculate, 
because the double-charge structure of the leptonic final state 
limits the number of partonic processes and total number of Feynman diagrams for each process.
Nonetheless, it posseses all features of VBS at the LHC and is thus representative of other VBS signatures.
Therefore, this process is the ideal candidate for a comparative study of the different simulation tools.

In the last few years, several next-to-leading order (NLO) computations have become available for both the VBS process~\cite{Jager:2006zc,Jager:2006cp,Bozzi:2007ur,Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
All these VBS computations rely on various approximations, typically neglecting contributions which are expected to be small under realistic experimental setups~\cite{Oleari:2003tc,Denner:2012dz}. Recently, the complete NLO corrections to $\PW^+\PW^+$ have been evaluated in Ref.~\cite{Biedermann:2017bss}, making it possible for the first time to study in detail the quality of the VBS approximations used in most tools.

{\bf MZ: we can remove the following sentence, up to the citation of Oleari}
Apart from Ref.~\cite{Biedermann:2017bss}, no detailed comparison of the VBS approximations have been carried out beyond the leading-order~\cite{Oleari:2003tc}.

>>>>

Vector-boson scattering (VBS) at a hadron collider 
usually refers to the interaction of massive vector-bosons ($\PW^\pm,\PZ$),
radiated by partons (quarks) of the incoming protons, 
which in turn are deflected from the beam direction 
and enter the volume of the particle detectors.
As a consequence, the typical signature of VBS events
is characterised by two energetic jets 
and four fermions,
originating from the decay of the two vector bosons.
Among the possible diagrams,
the scattering process can be mediated by a Higgs boson
and involves in particular their longitudinal component.
The interaction of longitudinally polarised bosons is of particular interest, 
because the corresponding matrix elements feature unitarity cancellations 
that strongly depend on the actual structure of the Higgs sector.
A detailed study of this class of processes will therefore further constrain the Higgs couplings 
at a very different energy scale with respect to the Higgs boson mass,
and hint at, or exclude, non-Standard Model behaviours.

The VBS process involving two same-sign $\PW$ bosons has the largest signal-to-background ratio at the LHC of all the VBS processes:
evidence for it was found at the centre-of-mass energy of $8~\TeV$ already~\cite{Aad:2014zda,Khachatryan:2014sta},
and it has been recently observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} 
at $13\TeV$ as well.
Presently, the measurements of VBS processes are limited by statistics, but the situation will change in the near future.
On the theoretical side, 
it is thus of prime importance to provide predictions with systematic uncertainties
at least comparable to the current and envisaged experimental precision~\cite{CMS:2016rcn}.

$\PW^+\PW^+$ scattering is also the simplest VBS process to calculate, 
because the double-charge structure of the leptonic final state 
limits the number of partonic processes and total number of Feynman diagrams for each process.
Nonetheless, it possesses all features of VBS at the LHC and is thus representative of other VBS signatures.
Therefore, this process is the ideal candidate for a comparative study of the different simulation tools.

In the last few years, several next-to-leading order (NLO) computations have become available for both the VBS process~\cite{Jager:2006zc,Jager:2006cp,Bozzi:2007ur,Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
All these VBS computations rely on various approximations, typically neglecting contributions which are expected to be small under realistic experimental setups~\cite{Denner:2012dz,Oleari:2003tc}.
Recently, the complete NLO corrections to $\PW^+\PW^+$ have been evaluated in Ref.~\cite{Biedermann:2017bss}, making it possible for the first time to study in detail the quality of the VBS approximations at NLO QCD.

% {\bf MZ: we can remove the following sentence, up to the citation of Oleari}
% Apart from Ref.~\cite{Biedermann:2017bss}, no detailed comparison of the VBS approximations have been carried out beyond the leading-order~\cite{Oleari:2003tc}.

### 2018-02-20 Draft/process.tex
Many changes from Ansgar and Mathieu

We now turn to discuss the various approximations which are implemented in computer programs for the EW contribution at
$\mathcal{O}{\left(\alpha^{6}\right)}$. Since we are mostly interested in 
the scattering of two $\PW$ gauge bosons, which includes the quartic gauge-boson vertex, may appear justified to approximate the 
full process by considering just those diagrams which contain the $2\rightarrow 2$ scattering process as a subpart.
However, this set of contributions is not automatically gauge invariant. In order ensure gauge invariance, one 
an on-shell projection of the incoming and outgoing $\PW$ bosons should be performed {\bf MZ CITE}.
Unfortunately, the former momenta are space-like and thus a simple on-shell projection is not possible.
Instead, one can keep the $\PW$ boson legs connected to the external quark line off-shell while the ones connected 
to the final-state leptons, which are already time-like, are put on-shell. {\bf MZ is this still gauge invariant? if so, one should change 
the sentence above ``In order to ensure..''}
Then the polarisation of the gauge boson is accommodated for following for example the implementations of Refs.~\cite{Kuss:1995yv,Accomando:2006hq}.
Such an approximation is usually called effective vector-boson approximation (EVBA) \cite{Dawson:1984gx,Duncan:1985vj,Cahn:1983ip}.

An improvement of such an approximation consists 
in considering all $t$- and $u$- diagrams and squaring them separately, neglecting interference contributions between the two classes.
These interferences are expected to be small in the VBS fiducial region, as they are both phase-space and colour suppressed~\cite{Oleari:2003tc}.
The $s$-channel squared diagrams and any interferences between them and the  $t/u$-channels are also discarded.
This approximation is often called $t$-/$u$- approximation, VBF, or even VBS approximation.
We will adopt the latter denomination in the following of the article.
%Such an approximation is implemented at LO in the computer codes {\sc Bonsay} \AK{CITATIONS} and the {\sc Powheg-Box}~\cite{Alioli:2010xd}.
This approximation is gauge-invariant, a fact that can be appreciated by considering the two incoming quarks as belonging to two different copies of the 
$\rm{SU}(3)$ gauge group.

@@

{\bf MZ: why are we changing here the notation from $\alpha$ to $g$????}
In fact, when considering the full one-loop amplitude of order $\mathcal{O}(g_{\rm s}^2 g^6)$ and its corresponding real QCD radiation, 
other contributions of EW origin have to be added.
Indeed, in order to cancel all infrared (IR) divergences arising, also one-loop amplitudes of order $\mathcal{O}(g^8)$ of EW type and their corresponding QED radiations have to be included.
The full computation of order $\mathcal{O}{\left(\alphas \alpha^{6}\right)}$ consists thus not only of QCD-type corrections but also of EW ones. 
%Such predictions are provided by the combination {\sc MoCaNLO+Recola} as published in Ref.~\cite{Biedermann:2017bss}.

>>>>

We now turn to discuss the various approximations which are implemented in computer programs for the EW contribution at
$\mathcal{O}{\left(\alpha^{6}\right)}$. Since we are mostly interested in 
the scattering of two $\PW$ gauge bosons, which includes the quartic gauge-boson vertex, may appear justified to approximate the 
full process by considering just those diagrams which contain the $2\rightarrow 2$ scattering process as a subpart.
However, this set of contributions is not gauge invariant.
In order ensure gauge invariance, an on-shell projection of the incoming and outgoing $\PW$ bosons should be performed {\bf MZ CITE}.
Unfortunately, the former momenta are space-like and thus a simple on-shell projection is not possible.
Instead, one can keep the $\PW$ boson legs connected to the external quark line off-shell while the ones connected 
to the final-state leptons, which are already time-like, are put on-shell. \ZM{is this still gauge invariant? if so, one should change 
the sentence above ``In order to ensure..''}
Then the polarisation of the gauge boson is accommodated following for example the implementations of Refs.~\cite{Kuss:1995yv,Accomando:2006hq}.
Such an approximation is usually called effective vector-boson approximation (EVBA) \cite{Dawson:1984gx,Duncan:1985vj,Cahn:1983ip}.

An improvement of such an approximation consists 
in considering all $t$- and $u$-channel diagrams and squaring them separately, neglecting interference contributions between the two classes.
These interferences are expected to be small in the VBS fiducial region, as they are both phase-space and colour suppressed~\cite{Oleari:2003tc}.
The $s$-channel squared diagrams and any interferences between them and the  $t/u$-channels are also discarded.
This approximation is often called $t$-/$u$- approximation, VBF, or even VBS approximation.
We will adopt the latter denomination in the following of the article.
%Such an approximation is implemented at LO in the computer codes {\sc Bonsay} \AK{CITATIONS} and the {\sc Powheg-Box}~\cite{Alioli:2010xd}.
This approximation is gauge-invariant, a fact that can be appreciated by considering the two incoming quarks as belonging to two different copies of the $\rm{SU}(3)$ gauge group.

@@

When considering the full one-loop amplitude of order $\mathcal{O}(g_{\rm s}^2 g^6)$ squared with the tree amplitude of order $\mathcal{O}(g^6)$, not only real QCD radiation but also QED ones have to be included in order cancel IR singularities.
But all IR singularities related to photon emissions are not cancelled by the above mentioned virtual corrections.
Another type of virtual corrections have to incorporated, namely the one-loop amplitudes of order $\mathcal{O}(g^8)$ interfered with the tree-level ones of order $\mathcal{O}(g_{\rm s}^2 g^4)$.
Hence the full NLO corrections of order $\mathcal{O}{\left(\alphas \alpha^{6}\right)}$ consist not only of QCD-type corrections but also of EW ones \cite{Biedermann:2017bss}.
\MP{@MZ g. gs are for amplitude and alpha, alphas for matrix element squared.}
%Such predictions are provided by the combination {\sc MoCaNLO+Recola} as published in Ref.~\cite{Biedermann:2017bss}.

### 2018-02-20 Draft/scanLO.tex
Many changes from Ansgar and Mathieu

In Fig.~\ref{fig:ratio2d_LO}, the ratio of double-differential cross sections in the plane $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ is shown.
Two plots are displayed: the ratio of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation, respectively.
In the first case, the approximation is good within $\pm10\%$ over the whole range apart in the low invariant-mass region at both low and large rapidity difference.
The low rapidity difference region possesses remnants of the tri-bosons contributions that peek at the an di-jet invariant mass around the W-boson mass.
It is therefore expected that the $|t|^2 + |u|^2$ approximation fails in this region.
The second plot, where the $|s|^2 + |t|^2 + |u|^2$ approximation is considered, displays a better behaviour in the previously mentioned region.
The full calculation is approximated at the level of $\pm5\%$ apart in the region where $\Delta y_{\Pj\Pj} < 2$.
\AK{What are the MC error on these plots?}
\MP{@AK: I changed some stuffs in the text to justify the plot range}

\begin{figure}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/ratio_tu.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
\caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, |\Delta y_{\Pj\Pj}| \right)$ at LO \emph{i.e.}\ order $\mathcal{O}(\alpha^6)$.
Ratio of approximated squared amplitudes over the full matrix element.
The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (top) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (bottom).
The cuts applied are the one of of Sec.~\ref{subsec:inputpar} and no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.} 
\label{fig:ratio2d_LO}
\end{figure}
% As explained previously, the low di-jet invariant mass and low jet rapidity separation regions are dominated by tri-boson production.

>>>>

In Fig.~\ref{fig:ratio2d_LO}, ratios of double-differential cross sections in the plane $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ is shown.
Two plots are displayed: the ratios of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation.
In the first case, the approximation is good within $\pm10\%$ over the whole range apart in the low invariant-mass region at both low and large rapidity difference.
The low rapidity difference region possesses remnants of the tri-bosons contributions that peak at di-jet invariant mass around the W-boson mass.
It is therefore expected that the $|t|^2 + |u|^2$ approximation fails in this region.
The second plot, where the $|s|^2 + |t|^2 + |u|^2$ approximation is considered, displays a better behaviour in the previously mentioned region.
The full calculation is approximated at the level of $\pm5\%$ apart in the region where $\Delta y_{\Pj\Pj} < 2$.
\AK{What are the MC error on these plots?}
\MP{@AK: I changed some stuffs in the text to justify the plot range}

\begin{figure*}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/ratio_tu.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
\caption{Ratio of cross sections per bin in the plan $\left(m_{\Pj\Pj}, |\Delta y_{\Pj\Pj}| \right)$ at LO \emph{i.e.}\ order $\mathcal{O}(\alpha^6)$.
Ratio of approximated squared amplitudes over the full matrix element.
The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).
The cuts applied are the one of of Sec.~\ref{subsec:inputpar} and no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.} 
\label{fig:ratio2d_LO}
\end{figure*}
% As explained previously, the low di-jet invariant mass and low jet rapidity separation regions are dominated by tri-boson production.
